Title here

### 2016-12-16 portfolio/text/ms.Rmd
Edits

We evaluated trends in revenue and diversification over time for individuals
fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A). The
majority (70--90%) of fishers hold single permits, with a slight increase in
single-permit holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to halibut or salmon permit holders --- compared to other
fisheries, halibut permit holders are more likely to hold halibut plus other
permits, whereas salmon permit holders are more likely to hold only one permit
(Fig. \ref{fig:ts}C). Despite making up only 10--30% of the individuals,
multiple permit holders earn approximately half the overall revenue (Fig.
\ref{fig:ts}B). The mean effective fished species diversity of this revenue
declined somewhat from 1980--2000 but has since remained steady (Fig.
\ref{fig:ts}D). However, this trend appears to be driven by an increase in
salmon specialists in the 1980s and 1990s --- the trend disappears if salmon
license holders are excluded (Fig. \ref{fig:ts}D).

Individual revenue variability decreases exponentially with higher mean fished
species diversity across permit sets (Fig. \ref{fig:across}). Controlling for
effort, strategies with one unit higher mean effective species diversity had on
average `r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. This
pattern looks qualitatively similar with or without individuals targeting
salmon. As examples, variability was highest for the herring roe gillnet and
king crab fisheries. Most of the strategies with the lowest estimated revenue
variability combined halibut with a salmon permit and had high levels of fished
species diversity (Fig. \ref{fig:across}).

Comparing single permit holders to individuals holding that same permit plus
additional permits illustrates the expected reduction in revenue variability
from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\ref{fig:spoke-all}). For example, individuals fishing a halibut longline
permit plus one additional permit always had lower expected revenue variability
compared to individuals fishing only a halibut longline permit (median reduction
of `r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually increased expected revenue, although the permits
themselves represent a significant expense (e.g. ~\$192K USD for a king and
tanner crab permit in Southeast Alaska in 2016;
<https://www.cfec.state.ak.us/pmtvalue/X_K69A.HTM>).

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort, specializing tends to be
associated with increased revenue (Fig. \ref{fig:within}; Fig. S\ref{fig:fe},
Fig. S\ref{fig:re}) but also increased variability. On average, there is a ~0.5%
increase in the year-to-year revenue ratio per 1% decrease in species diversity,
and across strategies, `r g2_dens`% of the probability density supports
a positive relationship between specialization and revenue.

However, adjusting (increasing or decreasing) an individual's fished species
diversity within the constraints of a permit set tends to be associated with
greater expected variability or uncertainty in year-to-year revenue (Fig.
\ref{fig:within} strategies above 0; Figs. S\ref{fig:fe}, \ref{fig:re},
\ref{fig:mirror}). This effect was strongest for individuals with a halibut
permit or halibut and sablefish permits. Individuals with these strategies
experienced a ~2% increase in variability for a 1% change in the year-to-year
ratio of species diversity (Fig. \ref{fig:within}). Becoming more generalized in
species diversity also leads to increased revenue variability (Fig.
S\ref{fig:mirror}A), suggesting that the act of changing strategies is
a contributor to increased variability of revenue. This benefit of specializing
is most apparent after accounting for fishing effort (Fig. S\ref{fig:noeffort}).

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994, which potentially confounds our estimates of the
effect of diversity and a major regulatory change. We refit our models allowing
all strategy-level effects to vary separately before and after the introduction
of IFQs for strategies involving halibut and sablefish permits. The introduction
of IFQs reduced variability by ~25% (XX--XX 95% CI) for individuals with only
halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

@@

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies with a diversity of assets provide substantial benefits
over strategies with lower diversity [REFS]. However, the ability to effectively
diversify in practice is limited by regulation and market forces. Here we
document the effect of changing species diversity on revenue and revenue
variability across three scale. Each scale reflects individual-level choices
that produce varied levels of species diversity. We find that individuals
fishing permit sets that allow high levels of species diversity tend to have
lower revenue variability. Adding an additional fisheries permit usually
increases revenue and decreases revenue variability. However, within the
constraints of a permit and accounting for effort, specializing (reducing
species diversity) tends to increase revenue and specializing or generalizing
tends to be associated with greater revenue variability, with considerable
differences across fisheries. Thus, the most effective mechanism by which
species diversity can lower revenue variability for individual fishers ---
switching or adding fishing permits --- is often costly, limited by regulations,
and consequently unavailable to many individuals in practice.

>>>>

We evaluated trends in revenue and diversification over time for individuals
fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A). The
majority (70--90%) hold single permits, with a slight increase in single-permit
holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is most sensitive to
halibut or salmon permit holders --- compared to other fisheries, halibut permit
holders are more likely to hold halibut plus other permits, whereas salmon
permit holders are more likely to hold a single permit (Fig. \ref{fig:ts}C).
Despite making up only 10--30% of the individuals, multiple permit holders earn
approximately half the overall revenue (Fig. \ref{fig:ts}B). The mean effective
species diversity of this revenue declined somewhat from 1980--2000 but has
since remained steady (Fig. \ref{fig:ts}D). However, this trend appears largely
driven by an increase in salmon specialists in the 1980s and 1990s --- the trend
disappears if salmon license holders are excluded (Fig. \ref{fig:ts}D).

Individual revenue variability decreases exponentially with higher mean fished
species diversity across permit sets (Fig. \ref{fig:across}). Controlling for
effort, strategies with one unit higher mean effective species diversity had on
average `r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower variability. This
pattern looks qualitatively similar with or without individuals targeting
salmon. As examples, variability was highest for the herring roe gillnet and
king crab fisheries. Most strategies with the lowest estimated revenue
variability combined halibut with a salmon permit and had high levels of fished
species diversity (Fig. \ref{fig:across}).

Comparing single permit holders to individuals holding that same permit plus
additional permits illustrates the expected reduction in revenue variability
from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\ref{fig:spoke-all}). For example, individuals fishing a halibut permit plus
one additional permit always had lower expected revenue variability compared to
individuals fishing only a halibut permit (median reduction of `r
100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually increased expected revenue, although the permits
themselves represent a significant expense (e.g. ~\$192K USD for a king and
tanner crab permit in Southeast Alaska in 2016 REF;
<https://www.cfec.state.ak.us/pmtvalue/X_K69A.HTM>).

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort, specializing tends to be
associated with increased revenue but also increased variability (Fig.
\ref{fig:within}; Figs S\ref{fig:fe}, S\ref{fig:re}, S\ref{fig:noeffort}). On
average, there is a ~0.5% increase in the year-to-year revenue ratio per 1%
decrease in species diversity, and across strategies, `r g2_dens`% of the
probability density supports a positive relationship between specialization and
revenue.

<!--This benefit of specializing is most apparent after accounting for fishing
effort ().-->

However, changing (increasing or decreasing) an individual's fished species
diversity within the constraints of a permit set tends to be associated with
greater expected variability or uncertainty in year-to-year revenue (Fig.
\ref{fig:within} strategies above zero; Figs. S\ref{fig:fe}, S\ref{fig:re},
S\ref{fig:mirror}). This effect was strongest for individuals with a halibut
permit or halibut and sablefish permits. Individuals with these strategies
experienced a ~2% increase in variability for a 1% change in the year-to-year
ratio of species diversity (Fig. \ref{fig:within}). Becoming more generalized in
species diversity also leads to increased revenue variability (Fig.
S\ref{fig:mirror}A), suggesting that the act of changing strategies is
a contributor to increased variability of revenue.

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994, which potentially confounds our estimates with
a major regulatory change. Therefore, we refit our models allowing all
strategy-level effects to vary separately before and after the introduction of
IFQs for strategies involving halibut and sablefish permits. The introduction of
IFQs reduced variability by ~25% (XX--XX 95% CI) for individuals with only
halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

@@

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies with a diversity of assets provides substantial
benefits over strategies with lower diversity [REFS]. However, the ability to
effectively diversify in practice is limited by regulation and market forces.
Here we document the effect of changing species diversity on revenue and revenue
variability across three scale. Each scale reflects individual-level choices
that produce varied levels of species diversity. We find that individuals
fishing permit sets that allow high levels of species diversity tend to have
lower revenue variability. Adding an additional fisheries permit usually
increases revenue and decreases revenue variability. However, within the
constraints of a permit and accounting for effort, specializing (reducing
species diversity) tends to increase revenue and specializing or generalizing
tends to be associated with greater revenue variability, with considerable
differences across fisheries. Thus, the most effective mechanism by which
species diversity can lower revenue variability for individual fishers ---
switching or adding fishing permits --- is often costly, limited by regulations,
and consequently unavailable to many individuals in practice.
